% !TEX program = xelatex

\documentclass{muratcan_cv}

\setname{Ali}{Rahimi}
\setaddress{Esfahan/Iran}
\setmobile{+989135732644}
\setmail{alirahimii@protonmail.com}
\setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/ali-rahimi-50b20999} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://lrhm.github.io/react-portfolio} %you can play with color of the template (red is also nice..)
\setthemecolor{red} %you can play with color of the template (red is also nice..)
% \setmailto{mailto:alirahimii@protonmail.com}

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{%
I'm a Software Engineer. Assign me with some tasks, I'll find the solutions and get it done.
With 4+ years of experience in develpement of Native Android Applications with the new stacks such as Kotlin, JetPackComponents (MVVM/ROOM/DATABINDING/etc), Dependency Injection(Dagger), Dataflow(Retrofit/Moshi/Coroutines) and etc.
}
%
%Education
\section{Education} 

\hspace{0.2em}


    \datedexperience{Isfahan Univercity of Technology}{2013-2019} 
    \explanation{B.Sc. in Software Engineering} 
     \explanationdetail{
     Course Work: Software Engineering Principals(Design, Architecture, OOP, etc) Data Structure, OS Architecture, Theory of Formal Languages(Compilers, Automata), Databases(SQL/noSQL), Computer Networks(IP/UDP/TCP/HTTP), Network Security(SSL,RSA,AES), IT Engineering, Statistics, AI, Computer Graphics, Economics, Microprocessors.    }

     
     
     

%
% Experience
\section{Experience}
    %
  
    \hspace{0.2em}

    \datedexperience{Full front-end Android Developer}{Sep 2014 - March 2015} 
    \explanation{PulseCo, Freelancer, IR} 
    \explanationdetail{Pantomime Game/Application with cool UX and UI written in Java for android 2.1 to 4.0. The APK still works perfectly in android 10 !}
    %
    \datedexperience{iOS Developer}{May 2015 - August 2015 } 
    \explanation{PulseCo, Freelancer, IR} 
    \explanationdetail{I learned native iOS development with Swift by developing an existing android application to iOS. I really liked and appreciated the Apple Architecture Design guidelines (MVC)}
    %
    \datedexperience{Full front-end Android Developer}{Nov 2015 - July 2016} 
    \explanation{TreeCo, Freelancer, IR} 
    \explanationdetail{
    Android Online and Offline Game/Application written in Java. Key features: Notifications, Restfull and Web Sockets Communication With Server, Registration/Friend Management/Chat, Encrypted Coin System, Analytics and etc.     }
    %
    \datedexperience{Front-end Android Developer}{Oct 2016 - Dec 2016 } 
    \explanation{Remote Freelancer, Malaysia} 
    \explanationdetail{ %
     I implemented some basic data flow, authentication, subscribing to a payment plan and actual paying functionality with PayPall or Cards.     }
    %

    \datedexperience{FullStack Developer}{March 2019 - August 2019} 
    \explanation{Bachelor Project} 
    \explanationdetail{Persian Sign Language Learning Assistant Android Application for children with the use of Visual Learning techniques by providing videos and images. New learning modules could be added to the existing app from a node js server.     }

    %
    \datedexperience{Full front-end Android and Android TV Developer}{August 2019 - October 2020} 
    \explanation{Remote Freelancer, EU} 
    \explanationdetail{
        Complex Android and Android TV Application with a focus on the code quality and software architecture.
        Stack: Kotlin,MVVM,Databiding,RoomDB,WorkManager,Retrofit,Dependency Injection(Dagger) and Kotlin Coroutines. 
    Worked and communicated in English with a European company.   }
%
   

    %
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  Kotlin \cpshalf Java \cpshalf SQL  \ \ \textbf{\emph{Familiar:}} \ \  Javascript \cpshalf Swift \cpshalf Python \cpshalf C++ \cpshalf Bash}}
    %
    \newcommand{\skilltwo}{\createskill{Software Development}{User-Centric Approach to Design Apps \cpshalf OOP \cpshalf GIT \cpshalf LINUX \cpshalf Scrum \cpshalf Architecture Design}}
    %
    \newcommand{\skillthree}{\createskill{Android Dev}{Kotlin \cpshalf MVVM \cpshalf JetPackComponents \cpshalf Dependency Injection \cpshalf Clean Architecture}}
    %
    \newcommand{\skillfour}{\createskill{Web/Learning}{React \cpshalf Node \cpshalf Apollo \cpshalf Nextjs}}
    %
    \newcommand{\skillfive}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Farsi \ \ \textbf{\emph{Fluent:}} \ \ English \ \ \textbf{\emph{Beginner:}} \ \  Japanese }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive}
%
% Experience
% \section{Extra}
%     \newcommand{\extraone}{%
%     \lipsum[1][7-8]\par %replace this part with actual text
%     }
%     %
%     \newcommand{\extratwo}{%
%     \lipsum[1][9-10]\par %replace this part with actual text
%     }
%     %
%     \newcommand{\extrathree}{%
%     \lipsum[1][11-12]%replace this part with actual text
%     }
%     %
%     \newcommand{\listofextras}{\extraone, \extratwo, \extrathree}
%     %
%     \createbullets{\listofextras}
%
%Footnote
% \createfootnote
\end{document}
